---
title: "data analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(dplyr) 
```

## Load Data

```{r}
#install.packages('RJDBC')

## --------------------------------
## Sets Java Home
## --------------------------------
if (Sys.getenv("JAVA_HOME")!="")  Sys.setenv(JAVA_HOME="")


## --------------------------------
## Loads libraries
## --------------------------------
library(rJava)
options(java.parameters = "-Xmx8048m")
library(RJDBC)
library(DBI)


## --------------------------------
## Sets Java Home
## --------------------------------
if (Sys.getenv("JAVA_HOME")!="")
  Sys.setenv(JAVA_HOME="")


## --------------------------------
## Loads libraries
## --------------------------------
library(rJava)
options(java.parameters = "-Xmx8048m")
library(RJDBC)
library(DBI)


## --------------------------------
## General Variables
## --------------------------------
redShiftDriver <- JDBC("com.amazon.redshift.jdbc41.Driver", "RedshiftJDBC41-1.2.8.1005.jar", identifier.quote="`")
# put Redshift jar file in your home directory
resultSet <- data.frame()
username <- "zfan4"               ## Set VPCx / Redshift username - this is your J&J userID, for example mine is stong2  
password <- "19A3#a39F7py"            ## Set VPCx / Redshift password - this is the password you got from an encrypted email
rhealthDBName <- "saf"                ## Set dataset you want to connect to (full list provided here:  https://jnj.sharepoint.com/sites/PHM-GCSP-RND/RWE/Pages/rHEALTH-Database-Connectivity.aspx)


## --------------------------------
## Connection (do not change)
## --------------------------------
connectionString <- paste("jdbc:redshift://rhealth-prod-4.cldcoxyrkflo.us-east-1.redshift.amazonaws.com:5439/", rhealthDBName,"?ssl=true&sslfactory=com.amazon.redshift.ssl.NonValidatingFactory", sep="")
conn <- dbConnect(redShiftDriver, connectionString, username, password)


dbListTables(conn)

res <- dbSendQuery(conn,'select * from saf.scratch_ctsaf2.np_col_hipfx_ads_v9') ## CTSAF2 is my scratch space
data <- fetch(res,n = -1) 


```

The original data frame has 439248 observations, 247 variables.

```{r}
dim(data)
```



## Target Variables

**mortality_90** is a 0/1 flag indicating whether the patient died within 90 days post index discharge.
For the mortality, we have 380213 patients who are alive. 
```{r}
mean(data$mortality_90)
length(data$mortality_90)-sum(data$mortality_90)
```

**readm_flag** is a 0/1 flag indicating whether the patient was readmitted within 90 days post index discharge.   
For the readmission, we have 342935 patients who are not readmitted. 

```{r}
mean(data$readm_flag)
length(data$readm_flag)-sum(data$readm_flag)
```

**er_90days** is a 0/1 flag indicating ER visit within 90 days post index discharge.  
For the ER visit, we have 353680 patients who are not visited ER. 
```{r}
mean(data$er_90days)
length(data$er_90days)-sum(data$er_90days)
```


## Data About Patients

**Age**:
```{r}
summary(data$age)
ggplot(data, aes(x=age)) + 
  geom_histogram(binwidth = 5)
```

**gender**:
There is no unknown data in gender. 1 is male, 2 is female.
```{r}
sum(data$gndr_cd != 0)
ggplot(data, aes(x = gndr_cd)) +  
  geom_bar(aes(y = (..count..)/sum(..count..)))
```

**race**:
1 is white.

```{r}
ggplot(data, aes(x = bene_race_cd)) +  
  geom_bar(aes(y = (..count..)/sum(..count..))) 
```
##Important Features

```{r}
#creating variables
data_new <- data %>% mutate(#interval for age. Broken into 5 year intervals and under 65
                                      # correlation between age and age_interval?????
                                      age_interval = cut(age, breaks = c(0,65,70,75,80,85,90,95,100)),
                                      
                                      #creating a simpler version of diagnosis type
                                      diagnosis_type = case_when(substr(prncpal_dgns_cd,1,1) == "S" ~ "S",
                                                                 substr(prncpal_dgns_cd,1,1) == "M" ~ "M",
                                                                 TRUE ~ "Other"),
                                      
                                      #creating interval variable for length of stay
                                      
                                      
                                      los_interval = cut(index_los, breaks = c(0,1,2,5,10,20,40,80,160,320)),
                                      
                                      #making time series terms from dates
                                      
                                      #Index admission date
                                      month_clm = as.numeric(substr(clm_admsn_dt,6,7)),
                                      
                                      #Index discharge date
                                      month_dsch = as.numeric(substr(nch_bene_dschrg_dt,6,7)),
                                      
                                      
                                      season_clm = as.factor(case_when(month_clm <= 3 ~ "Winter",
                                                                       month_clm >= 10 ~ "Fall",
                                                                       month_clm > 3 & month_clm < 7 ~ "Spring",
                                                                       TRUE ~ "Summer")),
                                      
                                      
                                      season_dsch = as.factor(case_when(month_dsch <= 3 ~ "Winter",
                                                                        month_dsch >= 10 ~ "Fall",
                                                                        month_dsch > 3 & month_dsch < 7 ~ "Spring",
                                                                        TRUE ~ "Summer")),
                                      
                                      time_term_clm = as.numeric(substr(clm_admsn_dt,9,10)) + 
                                        month_clm * 30 + 365 * (yr_adm - min(yr_adm)),
                                      
                                      time_term_dsch = as.numeric(substr(nch_bene_dschrg_dt,9,10)) + 
                                        month_dsch * 30 + 365 * (yr_disch - min(yr_disch))
)

```


```{r}
summary(data_new$time_term_dsch  - data_new$time_term_clm)
ggplot(data_new, aes(x=time_term_dsch  - time_term_clm)) + 
  geom_histogram(binwidth = 5)

```
```{r}
summary(data$index_los)
ggplot(data, aes(x=index_los)) + 
  geom_histogram(binwidth = 5)
```

**clm_utlztn_day_cnt**:  
On an institutional claim, the number of covered days of care that are chargeable to Medicare facility utilization that includes full days, coinsurance days, and lifetime reserve days. It excludes any days classified as non-covered, leave of absence days, and the day of discharge or death.
```{r}
summary(data$clm_utlztn_day_cnt)
```
**clm_pps_cptl_drg_wt_num**:  
DRG weight
```{r}
unique(data$clm_pps_cptl_drg_wt_num)
```


**re_clm_pmt_amt**:  
Claim payment amount of the 1st readmission episode
```{r}
summary(data$re_clm_pmt_amt)
```
**disc_status**:  
Discharge status from index episode
```{r}
ggplot(data, aes(x = disc_status)) +  
  geom_bar(aes(y = (..count..)/sum(..count..))) 
```


## Entries of scores

cci_score_1825_days_b is **CCI score**: quantifies an individual’s burden of disease and corresponding 1-year mortality risk.

```{r}
length(unique(data$cci_score_1825_days_b))
unique(data$cci_score_1825_days_b)
```
elix_score_1825_days_b is **Elixhauser Score**: A method for measuring patient comorbidity based on ICD-9-CM and ICD-10 diagnosis codes found in administrative data.

```{r}
length(unique(data$elix_score_1825_days_b))
unique(data$elix_score_1825_days_b)
```
fci_score_1825_days_b is **FCI Score**: is calculated by looking at the ratio of the required renewal cost of the current year to the current building replacement value

```{r}
length(unique(data$fci_score_1825_days_b))
unique(data$fci_score_1825_days_b)
```

## Empty Characters

at_physn_upin: NPIs replaced UPINs as the standard provider identifiers beginning in 2007. The UPIN is almost never populated after 2009.

NPI: On an institutional claim, the national provider identifier (NPI) number assigned to uniquely identify the physician who has overall responsibility for the beneficiary's care and treatment.


```{r}
unique(data$at_physn_upin)
unique(data$op_physn_upin)
```


## Intresting Variables

cont_enroll_flag_1825b_89f is a 0/1 flag indicating that the patient is continuously enrolled for 1825 days in baseline and 90 days in follow-up. All entries is '1'.

```{r}
mean(data$cont_enroll_flag_1825b_89f)
```

hmo_enroll_flag_1825b_89f is a 0/1 flag indicating that the patient is continuously enrolled with HMO for 1825 days in baseline and 90 days in follow-up. All entries is '0'.

```{r}
mean(data$hmo_enroll_flag_1825b_89f)
```
These variables has variance 0. 

```{r}
summary(data$re_clm_pmt_amt)
```
